---
title: "{{report_title}}"
author: "{{author}}"
date: "`r if (nzchar(params$date)) params$date else format(Sys.Date())`"
format:
  docx:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 5
    reference-doc: reference.docx
resource-path:
  - "."
  - ".."
  - "../.."
params:
  date: ""
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.width = 8, fig.height = 5, dpi = 150
)
knitr::opts_knit$set(root.dir = here::here())

suppressPackageStartupMessages({
  library(dplyr)
  library(ggplot2)
  library(flextable)
  library(here)
  library(readr)
})

fig <- function(file) file.path("output", "figures", file)
tbl <- function(file) here::here("output", "tables", file)
mod <- function(file) here::here("output", "models", file)

read_csv_safe <- function(p) suppressMessages(readr::read_csv(p, show_col_types = FALSE))

# Inline-prose formatters for `r ...` chunks embedded in body text.
# fmt_p()        bare value: "0.042" or "<0.001"  (use inside tables or parenthesised lists)
# fmt_p_inline() operator + value: "= 0.042", "< 0.001", "<= 0.002"
#                pass op = "<=" for "p <= 0.042"; the < cap absorbs the operator
#                for tiny p so prose never reads "p <= < 0.001".
fmt_p <- function(p, d = 3) {
  if (is.na(p)) {
    return(NA_character_)
  }
  thr <- 10^(-d)
  if (p < thr) {
    paste0("<", formatC(thr, digits = d, format = "f"))
  } else {
    formatC(p, digits = d, format = "f")
  }
}

fmt_p_inline <- function(p, op = "=", d = 3) {
  if (is.na(p)) {
    return(NA_character_)
  }
  thr <- 10^(-d)
  if (p < thr) {
    paste0("< ", formatC(thr, digits = d, format = "f"))
  } else {
    paste0(op, " ", formatC(p, digits = d, format = "f"))
  }
}
```

# Executive Summary

(One-page synthesis. Replace this with bottom-line findings, key effect estimates with uncertainty, and recommendations.)

# Background and Objectives

(Scientific background, research questions, scope.)

# Data and Methods

## Data sources

(Source documentation; provenance; data quality.)

## Statistical methods

(Methods with citations for non-standard approaches; software versions; assumption checking; missing data handling.)

# Results

## Demographics

```{r tbl-demographics}
#| tbl-cap: "Participant characteristics by group."
table_one_path <- tbl("01_table_one.rds")
if (file.exists(table_one_path)) {
  readRDS(table_one_path) |>
    as_flex_table() |>
    flextable::set_table_properties(width = 1, layout = "autofit", align = "center") |>
    flextable::fontsize(size = 10, part = "all")
} else {
  flextable::flextable(data.frame(Note = "Build the table upstream and saveRDS to output/tables/01_table_one.rds."))
}
```

## Primary outcome

```{r fig-primary}
#| fig-cap: "Primary outcome trajectory by group."
primary_fig_path <- fig("01_primary.png")
if (file.exists(here::here(primary_fig_path))) {
  knitr::include_graphics(primary_fig_path)
} else {
  cat("Build the figure upstream and write to output/figures/01_primary.png.")
}
```

# Sensitivity Analyses

(Document robustness under alternative assumptions.)

# Limitations

(Honest acknowledgment of biases, precision constraints, generalisability.)

# Recommendations

(Actionable, prioritised, tied to findings; respect consultant-client boundary.)

# Reproducibility

```{r reproducibility}
sessionInfo()
```

# References

(Citations for non-standard methods, guidelines followed, background literature.)
